An Example Paper

### 2019-03-30 paper/paper.tex
Work on induction principle

\usepackage{cleveref}
\usepackage{entcsmacro}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{bussproofs}
\usepackage{stmaryrd}
\usepackage{cleveref}

@@

@@

% HoTT
\newcommand{\deprod}[3]{\prod_{#1 : #2} #3} % dependent product
\newcommand{\hset}{\type{hSet}} % sets
\newcommand{\0}{\textbf{0}} % empty type
\newcommand{\1}{\textbf{1}} % unit type
\newcommand{\inl}{\term{inl}} %left inclusion
\newcommand{\inr}{\term{inr}} % right inclusion
\newcommand{\prl}{\term{pr}_1} % first projection
\newcommand{\prr}{\term{pr}_2} % second projection
\newcommand{\pairTm}[2]{(#1 , #2)} % pairing
\newcommand{\weq}{\simeq} % weak equivalence
\newcommand{\setquot}[2]{#1 / #2} % quotient type
\newcommand{\transport}[2]{\function{transport}^{#1} #2} % transport
\newcommand{\classof}{\constructor{class}} % class construcor
\newcommand{\classeq}{\constructor{classeq}} % path between classes
\newcommand{\isaprop}[1]{\function{isaprop}(#1)} % a type is a set
\newcommand{\isaset}[1]{\function{isaset}(#1)} % a type is a set
\newcommand{\trunct}[1]{\lVert #1 \rVert} % propositional truncation
\newcommand{\truncel}[1]{| #1 |} % constructor of truncation
\newcommand{\depeq}[3]{#2 =_{#1} #3} % dependent equality type

@@

% Displayed algebras
\newcommand{\polydact}[2]{\overline{#1} \> #2}
\newcommand{\epdact}[2]{\overline{#1} \> #2}
\newcommand{\polydmap}[2]{\overline{#1} \> #2}

\def\lastname{Please list Your Lastname Here}
\begin{document}
\begin{frontmatter}
  \title{An Example Paper} \author{My
    Name\thanksref{ALL}\thanksref{myemail}}
  \address{My Department\\ My University\\
    My City, My Country} \author{My Co-author\thanksref{coemail}}
  \address{My Co-author's Department\\My Co-author's University\\
    My Co-author's City, My Co-author's Country} \thanks[ALL]{Thanks
    to everyone who should be thanked} \thanks[myemail]{Email:
    \href{mailto:myuserid@mydept.myinst.myedu} {\texttt{\normalshape
        myuserid@mydept.myinst.myedu}}} \thanks[coemail]{Email:
    \href{mailto:couserid@codept.coinst.coedu} {\texttt{\normalshape
        couserid@codept.coinst.coedu}}}
\begin{abstract} 
  This is a short example to show the basics of using the ENTCS style
  macro files.  Ample examples of how files should look may be found
  among the published volumes of the series at the ENTCS Home Page
  \texttt{http://www.elsevier.com/locate/entcs}.
\end{abstract}
\begin{keyword}
  Please list keywords from your paper here, separated by commas.
\end{keyword}
\end{frontmatter}
\section{Introduction}
\label{intro}

@@

\subsection{Displayed Algebras}
A displayed algebra is the input of the elimination rule.
This means that we have a dependent family and a dependent map over the point constructor.
Furthermore, dependent versions of the equations in the signature needs to hold.
To formulate these requirements more precisely, we need two preliminary definitions.
The first one gives an action of polynomials on type families while the second one interprets endpoints as dependent maps.

@@

\subsection{Obtaining Induction from Initiality}
Now suppose that we have some displayed algebra.
Our goal is to construct an algebra whose objects are dependent pairs.

Give the carrier and operation in plain text

\begin{lemma}
pr1 endpoint
\end{lemma}

\begin{lemma}
pr2 endpoint
\end{lemma}

All in all, we get the following construction.

\begin{theorem}
Total algebra and projection
\end{theorem}

\begin{proposition}
Map to total algebra which projects into identity is section.
\end{proposition}

Hence, to construct a HIT, it suffices to construct an initial object in the category of algebras.

\begin{corollary}

\end{corollary}

\section{Constructing the Initial Algebra}

@@

\section{Consequences}

@@

\section{Conclusion}

\begin{thebibliography}{10}\label{bibliography}
\bibitem{cy} Civin, P., and B. Yood, \emph{Involutions on Banach
    algebras}, Pacific J. Math. \textbf{9} (1959), 415--436.

\bibitem{cp} Clifford, A. H., and G. B. Preston, ``The Algebraic
  Theory of Semigroups,'' Math. Surveys \textbf{7}, Amer. Math. Soc.,
  Providence, R.I., 1961.

\bibitem{f} Freyd, Peter, Peter O'Hearn, John Power, Robert Tennent
  and Makoto Takeyama, \emph{Bireflectivity}, Electronic Notes in
  Theoretical Computer Science {\bf 1} (1995), URL:
  \href{https://www.sciencedirect.com/journal/electronic-notes-in-theoretical-computer-science/vol/1/suppl/C}
  {\texttt{http://www.elsevier.com/locate/entcs/volume1.html}}.

\bibitem{em2} Easdown, D., and W. D. Munn, \emph{Trace functions on
    inverse semigroup algebras}, U. of Glasgow, Dept. of Math.,
  preprint 93/52.

\bibitem{r} Roscoe, A. W., ``The Theory and Practice of Concurrency,''
  Prentice Hall Series in Computer Science, Prentice Hall Publishers,
  London, New York (1198), 565pp. With associated web site\\  
  \href{http://www.comlab.ox.ac.uk/oucl/publications/books/concurrency/}
  {\texttt{http://www.comlab.ox.ac.uk/oucl/publications/books/concurrency/}}.

\bibitem{s} Shehadah, A. A., ``Embedding theorems for semigroups with
  involution, `` Ph.D.  thesis, Purdue University, Indiana, 1982.

\bibitem{w} Weyl, H., ``The Classical Groups,'' 2nd Ed., Princeton U.
  Press, Princeton, N.J., 1946.

\end{thebibliography}

\end{document}

>>>>

\usepackage{cleveref}
\usepackage{entcsmacro}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{bussproofs}
\usepackage{stmaryrd}
\usepackage{cleveref}
\usepackage{listings}
\usepackage{coq}
\usepackage{color}
\usepackage{xcolor}

@@

\newcommand{\ie}{\emph{i.e.,} }
\newcommand{\cf}{\emph{c.f.} }
\newcommand{\eg}{\emph{e.g.,} }
\newcommand{\etal}{\emph{et~al.}}
\newcommand{\etc}{\emph{etc.}}
\newcommand{\wrt}{w.r.t.~}
\newcommand{\resp}{resp.~}
\newcommand{\loccit}{\emph{loc. cit.} }

@@

% HoTT
\newcommand{\deprod}[3]{\prod_{#1 : #2} #3} % dependent product
\newcommand{\desum}[3]{\sum_{#1 : #2} #3} % dependent sum
\newcommand{\hset}{\type{hSet}} % sets
\newcommand{\0}{\textbf{0}} % empty type
\newcommand{\1}{\textbf{1}} % unit type
\newcommand{\inl}{\term{inl}} %left inclusion
\newcommand{\inr}{\term{inr}} % right inclusion
\newcommand{\prl}{\term{pr}_1} % first projection
\newcommand{\prr}{\term{pr}_2} % second projection
\newcommand{\pairTm}[2]{(#1 , #2)} % pairing
\newcommand{\weq}{\simeq} % weak equivalence
\newcommand{\setquot}[2]{#1 / #2} % quotient type
\newcommand{\transport}[2]{\function{transport}^{#1} #2} % transport
\newcommand{\invP}[1]{(#1)^{-1}} % inverse of a path
\newcommand{\classof}{\constructor{class}} % class construcor
\newcommand{\classeq}{\constructor{classeq}} % path between classes
\newcommand{\isaprop}[1]{\function{isaprop}(#1)} % a type is a set
\newcommand{\isaset}[1]{\function{isaset}(#1)} % a type is a set
\newcommand{\trunct}[1]{\lVert #1 \rVert} % propositional truncation
\newcommand{\truncel}[1]{| #1 |} % constructor of truncation
\newcommand{\depeq}[3]{#2 =_{#1} #3} % dependent equality type

@@

% Displayed algebras
\newcommand{\polydact}[2]{\overline{#1} \> #2} % dependent action of polynomials on families
\newcommand{\epdact}[2]{\overline{#1} \> #2} % dependent action of endpoints
\newcommand{\polydmap}[2]{\overline{#1} \> #2} % action of polynomials on dependent maps
\newcommand{\total}[1]{\int #1} % total algebra of displayed algebra
\newcommand{\proj}[1]{\pi_1^{#1}} % projection homomorphism
\newcommand{\Ppl}[1]{\pi_1^{#1}} % dependent second projection, poly_pr2
\newcommand{\Ppr}[1]{\pi_2^{#1}} % dependent second projection, poly_pr2
\newcommand{\Epl}{\function{epr_1}} % first projection of endpoin action
\newcommand{\Epr}{\function{epr_2}} % first projection of endpoin action

% Examples of HITs
\newcommand{\Circ}{S^1} % circle
\newcommand{\base}{\constructor{base}} % base point of circle
\newcommand{\loopS}{\constructor{loop}} % base point of circle

\newcommand{\remove}{}

\def\lastname{Please list Your Lastname Here}
\begin{document}
\begin{frontmatter}
  \title{An Example Paper} \author{My
    Name\thanksref{ALL}\thanksref{myemail}}
  \address{My Department\\ My University\\
    My City, My Country} \author{My Co-author\thanksref{coemail}}
  \address{My Co-author's Department\\My Co-author's University\\
    My Co-author's City, My Co-author's Country} \thanks[ALL]{Thanks
    to everyone who should be thanked} \thanks[myemail]{Email:
    \href{mailto:myuserid@mydept.myinst.myedu} {\texttt{\normalshape
        myuserid@mydept.myinst.myedu}}} \thanks[coemail]{Email:
    \href{mailto:couserid@codept.coinst.coedu} {\texttt{\normalshape
        couserid@codept.coinst.coedu}}}
\begin{abstract} 
  This is a short example to show the basics of using the ENTCS style
  macro files.  Ample examples of how files should look may be found
  among the published volumes of the series at the ENTCS Home Page
  \texttt{http://www.elsevier.com/locate/entcs}.
\end{abstract}
\begin{keyword}
  Please list keywords from your paper here, separated by commas.
\end{keyword}
\end{frontmatter}
\section{Introduction}
\label{intro}
Homotopy type theory (HoTT) is a form of intensional type theory. 
It has semantics in the simplicial sets model \cite{simpset}, and types represent spaces, terms represent points, and equalities represent paths.
Furthermore, equality is proof relevant and we frequently talk about homotopies: paths between paths.

One of the main features of HoTT, is higher inductive types (HITs) \cite{hottbook}.
These are types generated by constructors for their points, paths, homotopies, and so on.
HITs have been used in numerous applications among which are homotopical patch theory \cite{AngiuliMLH16}. synthetic homotopy theory \cite{LicataF14,LicataS13,hottbook}, defining type theory within type theory \cite{AltenkirchK16}, constructive finiteness \cite{FruminGGW18}, and the partiality monad \cite{AltenkirchDK17}.

To get a feeling for what HITs are, let us look a some examples before looking at them more formally.

\lstset{language=Coq}
\setlength{\tabcolsep}{30pt}	
\begin{tabular}{ c c c }

\begin{lstlisting}[mathescape=true]
Inductive $\Circ$ :=
| $\base$ : $\Circ$
| $\loopS$ : $\base = \base$
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true]
Inductive $\trunct{A}$ :=
| $\truncel{\cdot}$ : $A \rightarrow \trunct{A}$
| $p$ : $\deprod{x, y}{\trunct{A}}{x = y}$
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true]
Inductive $H$ :=
| $c$ : $H \times H \rightarrow H$
| $p$ : $\deprod{x, y}{H}{c(x,y) = c(y,x)}$
\end{lstlisting}
\end{tabular}

The first one, $\Circ$, is the \emph{circle}.
It has a point, $\base$, and a path $\loopS : \base = \base$.
Since neither the point nor path constructors uses arguments from $\Circ$, this HIT is \emph{nonrecursive}.
The second, $\trunct{A}$, is the \emph{propositional truncation} of $A$.
This type is $A$ with all its points identified.
Note that the path constructor $p$ uses arguments from $\trunct{A}$, and thus this HIT is called \emph{recursive}.

The last example, CHANGE TO INTEGERS MODULO 2 (with recursive path constr)

Several schemes of HITs have already been developed.
Awodey \etal \ showed that the rules of inductive types \cite{dybjer1994inductive} in HoTT are equivalent to being a homotopy initial algebra \cite{AwodeyGS12}.
They extended this result to a class of HITs called \emph{W-suspensions} \cite{Sojakova15}.
Another scheme, quotient inductive-inductive types, was defined semantically by Altenkirch \etal \ and they prove initial algebra semantics \cite{AltenkirchCDKF18}.
Assuming UIP, Kaposi \etal \ constructed finitary QIITs as the syntax of a domain specific type theory \cite{KaposiKA19}, and they extended this scheme to higher inductive-inductive types \cite{KaposiK18}.
Basold \etal \ defined an external syntactic scheme for HITs with only point and path constructors \cite{BasoldGW17}.
Dybjer and Moenclaey defined a scheme allowing constructors for points, paths, and homotopies. and give its semantics in the groupoid model  \cite{DybjerM18,HofmannS94}.
Cavallo and Harper extend computational cubical type theory with a scheme for indexed cubical inductive types and proved canonicity \cite{AngiuliHW17,CavalloH19}.

Furthermore, the semantics of HITs also has been studied.
Coquand \etal \ provide the semantics of various higher inductive types, such as spheres, the torus, the truncation, and the pushout, in cubical type theory \cite{BezemCH13,CohenCHM16,CoquandHM18}.
On the other hand, Lumsdaine and Shulman also study the semantics of higher inductive types, but they use a semantic scheme (cell monads with parameters) and proof existence in sufficiently nice Quillen model categories \cite{lumsdaine2017semantics}.
Some recursive higher inductive types can be constructed from nonrecursive HITs.
Both Kraus and Van Doorn show that the propositional truncation can be constructed from non-recursive HITs \cite{Kraus16,Doorn16} and Rijke shows that every truncation can be constructed via non-recursive HITs \cite{rijke2017join}.

In this paper, we show that all finitary set-truncated HITs can be constructed with quotients and propositional truncations. 
This briefly means that all higher inductive types exist if a small number of simple ones exist.
Furthermore, we use this construction to deduce several properties of HITs such as uniqueness and that the path space is freely generated.
The latter result is similar to work by Kraus and Von Raumer \cite{KrausRaumer}.
Note that from this construction we can conclude that finitary set-truncated HITs can be constructed from non-recursive HITs.
Since quotients can be constructed from coequalizers and set truncations, we only need coequalizers and propositional/set truncations for this construction.

The main idea of the proof is to take advantage that the quotient is an adjoint functor \cite{RijkeS15} from setoids to sets.
To relate this to HITs, we first define schemes, which are an internalized version of the schema by Basold \etal \ \cite{BasoldGW17}, and categories of algebras on them.
Then we lift the quotient adjunction to an adjunction from algebras in setoids and algebras in sets.
Since initiality implies induction, it suffices to construct the initial setoid algebra for which we adapt the construction by Dybjer and Moenclaey \cite{moeneclaey2016schema,DybjerM18}.

All definitions and proofs in his paper are formalized over the UniMath library \cite{UniMath}.
The formalization is 4166 lines of code and it can be found on \url{https://github.com/nmvdw/SetHITs}.

We start in \Cref{sec:prelim} by recalling some definitions from HoTT and category theory required for the rest of the paper.
In \Cref{sec:signature}, we define signatures for higher inductive types and give a couple of examples.
Next we define algebras in both the categories of sets and setoids for such signatures in \Cref{sec:algebras}.
We define the induction principle of HITs via displayed algebras in \Cref{sec:induction} and we show that initial objects satisfy this principle.
\Cref{sec:construction} is the core of this paper and there we construct an adjunction between algebras in sets and setoids, which we use to construct the initial algebra in sets via the initial algebra in setoids.
We study the consequences of this construction in \Cref{sec:consequences} and in \Cref{sec:conclusion}, we conclude and discuss further work.

@@

\subsection{Displayed Algebras}
\label{ref:induction}
A displayed algebra is the input of the elimination rule.
This means that we have a dependent family and a dependent map over the point constructor.
Furthermore, dependent versions of the equations in the signature needs to hold.
To formulate these requirements more precisely, we need two preliminary definitions.
The first one gives an action of polynomials on type families while the second one interprets endpoints as dependent maps.

@@

\subsection{Obtaining Induction from Initiality}
The goal of this section is to obtain the induction principle from initiality.
This way it suffices construct an initial object of the signature to obtain a HIT.
To this end, we first define the total algebra $\total{Y}$ of a displayed $Y$ on $X$ together a projection $\proj{Y}$ to $X$.
Then we show that induction can be obtained by finding a section of the projection.
Since this is always possible if $X$ is initial, we conclude by saying that initial objects satisfy the induction principle.

We define the carrier of $\total{Y}$ by the dependent sum $\desum{x}{X}{Y \> x}$ and for brevity, we denote this by $\total{Y}$.
To show this is an algebra, we first need to define a map $c_{\total{Y}} : \semP{\pointc{\Sigma}} \> (\total{Y}) \rightarrow \total{Y}$.
The main idea is that we use the algebra map of $X$ for the first component and the algebra map of $Y$ for the second one.
We introduce an intermediate definition, which allows us to access the right data.

\begin{definition}
Let $P$ be a polynomial and let $Y$ be a family of sets on $X$.
We define a map
\[
\Ppl{P} : \semP{P} \> (\desum{x}{X}{Y \> x} \rightarrow X)
\quad \quad
\Ppl{P} \> x = \semP{\pointc{\Sigma}} \> \prl \> x
\]
We also define a map $\Ppr{P} : \deprod{x}{\semP{P} \> (\desum{x}{X}{Y \> x})}{\polydact{P}{Y} \> (\Ppl{P} \> x)}$ by induction on $P$.
\begin{itemize}
	\item $\Ppr{\C \> T} \> x  = x$;
	\item $\Ppr{\I} \> x = \prr \> x$;
	\item $\Ppr{\sumP{P}{Q}} \> (\inl x) = \Ppr{P} \> x$;
	\item $\Ppr{\sumP{P}{Q}} \> (\inr x) = \Ppr{Q} \> x$;
	\item $\Ppr{\prodP{P}{Q}} \> x = (\Ppr{P} \> x , \Ppr{Q} \> (\prr \> x))$.
\end{itemize}
\end{definition}

Now let $z : \semP{\pointc{\Sigma}} \> (\total{Y})$.
The first coordinate of $c_{\total{Y}} \> z$ is defined to be $\constrA{X}(\Ppl{P} \> x)$.
The second coordinate of $c_{\total{Y}} \> z$ is defined by $c_Y \> (\Ppl{P} \> x) \> (\Ppr{P} \> x)$.
The main challenge lies within proving the equations.

\begin{lemma}
For every endpoint $e : \ep{\pointc{\Sigma}}{P}{Q}$, we have
\[
\Epl : \semE{e} \> X \> (\Ppl{P} \> x) = \Ppl{Q}(\semE{e} \> (\total{Y}) \> x) 
\]
\[
\Epr : \epdact{e}{c_Y} \> (\Ppr{P} \> x) = \transport{\polydact{Q}{Y}}{\invP{\Epl}} \> (\Ppr{Q} \> (\semE{e} \> (\total{Y}) \> x))
\]
\end{lemma}

All in all, given a displayed algebra $Y$ on some algebra $X$, we get the \emph{total algebra} $\total{Y}$.
We also define an algebra homomorphism $\proj{Y} : \total{Y} \rightarrow X$, which sends $z$ to its first projection $\prl \> z$.
The reason why we care about this construction, is the following proposition.

\begin{proposition}
From an algebra homomorphism $f : X \rightarrow \total{Y}$ such that $\comp{f}{\proj{Y}}$ is the identity, we obtain a displayed algebra map from $X$ to $Y$.
\end{proposition}

Now suppose $X$ is an initial object in the category of algebras.
Then, due to initiality, we always have a map $f : X \rightarrow \total{Y}$, and the composition $\comp{f}{\proj{Y}} : X \rightarrow X$ must be the identity because of initiality as well.
Hence, we conclude

\begin{corollary}
If $X$ is an initial object in the category of algebras on $\Sigma$, then $X$ is a HIT for $\Sigma$.
\end{corollary}

\section{Constructing the Initial Algebra}
\label{sec:construction}

@@

\section{Consequences}
\label{sec:consequences}

@@

\section{Conclusion}
\label{sec:conclusion}

\cite{AhrensKS15}
\cite{AhrensL19}
\cite{mac2013categories}

\begin{thebibliography}{10}\label{bibliography}

	\bibitem{AltenkirchCDKF18}
	Thorsten Altenkirch, Paolo Capriotti, Gabe Dijkstra, Nicolai Kraus, and
	Fredrik~Nordvall Forsberg, \emph{{Quotient Inductive-Inductive Types}},
	Foundations of Software Science and Computation Structures - 21st
	International Conference, {FOSSACS} 2018, Held as Part of the European Joint
	Conferences on Theory and Practice of Software, {ETAPS} 2018, Thessaloniki,
	Greece, April 14-20, 2018, Proceedings, 2018, pp.~293--310.

	\bibitem{AltenkirchDK17}
	Thorsten Altenkirch, Nils~Anders Danielsson, and Nicolai Kraus,
	\emph{{Partiality, Revisited - The Partiality Monad as a Quotient
			Inductive-Inductive Type}}, Foundations of Software Science and Computation
	Structures - 20th International Conference, {FOSSACS} 2017, Held as Part of
	the European Joint Conferences on Theory and Practice of Software, {ETAPS}
	2017, Uppsala, Sweden, April 22-29, 2017, Proceedings, 2017, pp.~534--549.

	\bibitem{ahrens2019bicategories}
	Benedikt Ahrens, Dan Frumin, Marco Maggesi, and Niels van~der Weide,
	\emph{{Bicategories in Univalent Foundations}}, arXiv preprint
	arXiv:1903.01152 (2019).

	\bibitem{AwodeyGS12}
	Steven Awodey, Nicola Gambino, and Kristina Sojakova, \emph{{Inductive Types in
			Homotopy Type Theory}}, Proceedings of the 27th Annual {IEEE} Symposium on
	Logic in Computer Science, {LICS} 2012, Dubrovnik, Croatia, June 25-28, 2012,
	2012, pp.~95--104.

	\bibitem{AngiuliHW17}
	Carlo Angiuli, Robert Harper, and Todd Wilson, \emph{{Computational
			Higher-Dimensional Type Theory}}, Proceedings of the 44th {ACM} {SIGPLAN}
	Symposium on Principles of Programming Languages, {POPL} 2017, Paris, France,
	January 18-20, 2017, 2017, pp.~680--693.

	\bibitem{AltenkirchK16}
	Thorsten Altenkirch and Ambrus Kaposi, \emph{{Type Theory in Type Theory using
			Quotient Inductive Types}}, Proceedings of the 43rd Annual {ACM}
	{SIGPLAN-SIGACT} Symposium on Principles of Programming Languages, {POPL}
	2016, St. Petersburg, FL, USA, January 20 - 22, 2016, 2016, pp.~18--29.

	\bibitem{AhrensKS15}
	Benedikt Ahrens, Krzysztof Kapulkin, and Michael Shulman, \emph{{Univalent
			Categories and the Rezk Completion}}, Mathematical Structures in Computer
	Science \textbf{25} (2015), no.~5, 1010--1039.

	\bibitem{AhrensL19}
	Benedikt Ahrens and Peter~LeFanu Lumsdaine, \emph{{Displayed Categories}},
	Logical Methods in Computer Science \textbf{15} (2019), no.~1.

	\bibitem{AngiuliMLH16}
	Carlo Angiuli, Edward Morehouse, Daniel~R. Licata, and Robert Harper,
	\emph{{Homotopical Patch Theory}}, J. Funct. Program. \textbf{26} (2016),
	e18.

	\bibitem{BezemCH13}
	Marc Bezem, Thierry Coquand, and Simon Huber, \emph{{A Model of Type Theory in
			Cubical Sets}}, 19th International Conference on Types for Proofs and
	Programs, {TYPES} 2013, April 22-26, 2013, Toulouse, France, 2013,
	pp.~107--128.

	\bibitem{BasoldGW17}
	Henning Basold, Herman Geuvers, and Niels van~der Weide, \emph{{Higher
			Inductive Types in Programming}}, J. {UCS} \textbf{23} (2017), no.~1, 63--88.

	\bibitem{CohenCHM16}
	Cyril Cohen, Thierry Coquand, Simon Huber, and Anders M{\"{o}}rtberg,
	\emph{{Cubical Type Theory: A Constructive Interpretation of the Univalence
			Axiom}}, CoRR \textbf{abs/1611.02108} (2016).

	\bibitem{CavalloH19}
	Evan Cavallo and Robert Harper, \emph{{Higher Inductive Types in Cubical
			Computational Type Theory}}, {PACMPL} \textbf{3} (2019), no.~{POPL},
	1:1--1:27.

	\bibitem{CoquandHM18}
	Thierry Coquand, Simon Huber, and Anders M{\"{o}}rtberg, \emph{{On Higher
			Inductive Types in Cubical Type Theory}}, Proceedings of the 33rd Annual
	{ACM/IEEE} Symposium on Logic in Computer Science, {LICS} 2018, Oxford, UK,
	July 09-12, 2018, 2018, pp.~255--264.

	\bibitem{capriotti2017univalent}
	Paolo Capriotti and Nicolai Kraus, \emph{{Univalent Higher Categories via
			Complete Semi-Segal Types}}, Proceedings of the ACM on Programming Languages
	\textbf{2} (2017), no.~POPL, 44.

	\bibitem{DybjerM18}
	Peter Dybjer and Hugo Moeneclaey, \emph{{Finitary Higher Inductive Types in the
			Groupoid Model}}, Electr. Notes Theor. Comput. Sci. \textbf{336} (2018),
	119--134.

	\bibitem{dybjer1994inductive}
	Peter Dybjer, \emph{{Inductive Families}}, Formal aspects of computing
	\textbf{6} (1994), no.~4, 440--465.

	\bibitem{FruminGGW18}
	Dan Frumin, Herman Geuvers, L{\'{e}}on Gondelman, and Niels van~der Weide,
	\emph{{Finite Sets in Homotopy Type Theory}}, Proceedings of the 7th {ACM}
	{SIGPLAN} International Conference on Certified Programs and Proofs, {CPP}
	2018, Los Angeles, CA, USA, January 8-9, 2018, 2018, pp.~201--214.

	\bibitem{HofmannS94}
	Martin Hofmann and Thomas Streicher, \emph{{The Groupoid Model Refutes
			Uniqueness of Identity Proofs}}, Proceedings of the Ninth Annual Symposium on
	Logic in Computer Science {(LICS} '94), Paris, France, July 4-7, 1994, 1994,
	pp.~208--212.

	\bibitem{KaposiK18}
	Ambrus Kaposi and Andr{\'{a}}s Kov{\'{a}}cs, \emph{{A Syntax for Higher
			Inductive-Inductive Types}}, 3rd International Conference on Formal
	Structures for Computation and Deduction, {FSCD} 2018, July 9-12, 2018,
	Oxford, {UK}, 2018, pp.~20:1--20:18.

	\bibitem{KaposiKA19}
	Ambrus Kaposi, Andr{\'{a}}s Kov{\'{a}}cs, and Thorsten Altenkirch,
	\emph{{Constructing Quotient Inductive-Inductive Types}}, {PACMPL} \textbf{3}
	(2019), no.~{POPL}, 2:1--2:24.

	\bibitem{simpset}
	Chris Kapulkin and Peter~LeFanu Lumsdaine, \emph{{The Simplicial Model of
			Univalent Foundations (after Voevodsky)}}, 2012.

	\bibitem{Kraus16}
	Nicolai Kraus, \emph{{Constructions with Non-Recursive Higher Inductive
			Types}}, Proceedings of the 31st Annual {ACM/IEEE} Symposium on Logic in
	Computer Science, {LICS} '16, New York, NY, USA, July 5-8, 2016, 2016,
	pp.~595--604.

	\bibitem{KrausRaumer}
	Nicolai Kraus and Jakob von Raumer, \emph{{Path Spaces of Higher Inductive
			Types in Homotopy Type Theory}}, CoRR \textbf{abs/1901.06022} (2019).

	\bibitem{LicataF14}
	Daniel~R. Licata and Eric Finster, \emph{{Eilenberg-MacLane Spaces in Homotopy
			Type Theory}}, Joint Meeting of the Twenty-Third {EACSL} Annual Conference on
	Computer Science Logic {(CSL)} and the Twenty-Ninth Annual {ACM/IEEE}
	Symposium on Logic in Computer Science (LICS), {CSL-LICS} '14, Vienna,
	Austria, July 14 - 18, 2014, 2014, pp.~66:1--66:9.

	\bibitem{LicataS13}
	Daniel~R. Licata and Michael Shulman, \emph{{Calculating the Fundamental Group
			of the Circle in Homotopy Type Theory}}, 28th Annual {ACM/IEEE} Symposium on
	Logic in Computer Science, {LICS} 2013, New Orleans, LA, USA, June 25-28,
	2013, 2013, pp.~223--232.

	\bibitem{lumsdaine2017semantics}
	Peter~LeFanu Lumsdaine and Mike Shulman, \emph{{Semantics of Higher Inductive
			Types}}, arXiv preprint arXiv:1705.07088 (2017).

	\bibitem{mac2013categories}
	Saunders Mac~Lane, \emph{{Categories for the Working Mathematician}}, vol.~5,
	Springer Science \& Business Media, 2013.

	\bibitem{moeneclaey2016schema}
	H.~Moeneclaey.
	\newblock {A Schema for Higher Inductive Types of Level One and Its
		Interpretation}.
	\newblock {\em Internship report, supervised by Peter Dybjer, ENS
		Paris-Saclay}, 2016.

	\bibitem{rijke2017join}
	Egbert Rijke, \emph{{The Join Construction}}, arXiv preprint arXiv:1701.07538
	(2017).

	\bibitem{RijkeS15}
	Egbert Rijke and Bas Spitters, \emph{{Sets in Homotopy Type Theory}},
	Mathematical Structures in Computer Science \textbf{25} (2015), no.~5,
	1172--1202.

	\bibitem{Sojakova15}
	Kristina Sojakova, \emph{{Higher Inductive Types as Homotopy-Initial
			Algebras}}, Proceedings of the 42nd Annual {ACM} {SIGPLAN-SIGACT} Symposium
	on Principles of Programming Languages, {POPL} 2015, Mumbai, India, January
	15-17, 2015, 2015, pp.~31--42.

	\bibitem{hottbook}
	{The Univalent Foundations Program}, \emph{{Homotopy Type Theory: Univalent
			Foundations of Mathematics}}, \url{https://homotopytypetheory.org/book},
	Institute for Advanced Study, 2013.

	\bibitem{UniMath}
	Vladimir Voevodsky, Benedikt Ahrens, Daniel Grayson, et~al., \emph{{UniMath ---
			a computer-checked library of univalent mathematics}}, {available} at
	\url{https://github.com/UniMath/UniMath}.

	\bibitem{Doorn16}
	Floris van Doorn, \emph{{Constructing the Propositional Truncation using
			Non-Recursive HITs}}, Proceedings of the 5th {ACM} {SIGPLAN} Conference on
	Certified Programs and Proofs, Saint Petersburg, FL, USA, January 20-22,
	2016, 2016, pp.~122--129.	
\end{thebibliography}

%\begin{thebibliography}{10}\label{bibliography}
%\bibitem{cy} Civin, P., and B. Yood, \emph{Involutions on Banach
%    algebras}, Pacific J. Math. \textbf{9} (1959), 415--436.

%\bibitem{cp} Clifford, A. H., and G. B. Preston, ``The Algebraic
%  Theory of Semigroups,'' Math. Surveys \textbf{7}, Amer. Math. Soc.,
%  Providence, R.I., 1961.

%\bibitem{f} Freyd, Peter, Peter O'Hearn, John Power, Robert Tennent
%  and Makoto Takeyama, \emph{Bireflectivity}, Electronic Notes in
%  Theoretical Computer Science {\bf 1} (1995), URL:
%  \href{https://www.sciencedirect.com/journal/electronic-notes-in-theoretical-computer-science/vol/1/suppl/C}
%  {\texttt{http://www.elsevier.com/locate/entcs/volume1.html}}.

%\bibitem{em2} Easdown, D., and W. D. Munn, \emph{Trace functions on
%    inverse semigroup algebras}, U. of Glasgow, Dept. of Math.,
%  preprint 93/52.

%\bibitem{r} Roscoe, A. W., ``The Theory and Practice of Concurrency,''
%  Prentice Hall Series in Computer Science, Prentice Hall Publishers,
%  London, New York (1198), 565pp. With associated web site\\  
%  \href{http://www.comlab.ox.ac.uk/oucl/publications/books/concurrency/}
%  {\texttt{http://www.comlab.ox.ac.uk/oucl/publications/books/concurrency/}}.

%\bibitem{s} Shehadah, A. A., ``Embedding theorems for semigroups with
%  involution, `` Ph.D.  thesis, Purdue University, Indiana, 1982.

%\bibitem{w} Weyl, H., ``The Classical Groups,'' 2nd Ed., Princeton U.
%  Press, Princeton, N.J., 1946.

%\end{thebibliography}
\end{document}
